---
title: "Roman Emperors 13/08/2019"
output:
  html_document: 
    df_print: paged
    keep_md: true
always_allow_html: yes
---

# Data description

Information about Roman emperors such as their birth date and place, reign start and end, death cause and others.

# Import data and packages

```{r message=FALSE, warning=FALSE}
# emperors <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-13/emperors.csv")
# readr::write_csv(emperors, "emperors.csv")
emperors <- readr::read_csv("emperors.csv")

library(tidyverse)
library(treemapify)
```

# Data 

Since it's a small dataset, I'll look it with Rstudio Viewer.

```{r}
View(emperors)
```

Most of the data is date or categorical. I'm curious about how many different death causes and killers we have.

```{r}
emperors_ck <- emperors %>% 
  transmute(cause = factor(cause),
         killer = factor(killer))

summary(emperors_ck)
```

So we have just 7 death causes and some varied killer motives.


```{r}
emperors_ck <- emperors_ck %>% 
  transmute(parent = cause,
            id = killer) %>% 
  group_by(parent, id) %>% 
  summarise(value = n())
```


```{r}
ggplot(emperors_ck, aes(area = value, fill = parent, label = id, subgroup = parent))+
  geom_treemap() +
  geom_treemap_text(place = 'topleft', min.size = 8, reflow = T) +
  geom_treemap_subgroup_text(
    alpha = 0.5, place = 'bottomleft'
  ) +
  scale_fill_brewer(palette = 'Dark2') +
  theme(
    legend.position = 'none',
    title = element_text(colour = 'darkslategrey')
  ) +
  labs(title = 'Cause of death of Roman Emperors (26BC-395AC)')
```

