---
title: "Tidy Tuesday 20/08/2019"
output:
  github_document: 
    df_print: kable
always_allow_html: yes
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-08-13):

> This week's data is from Stockholm International Peace Research Institute, by way of data is plural with credit to Jesus Castagnetto for sharing the dataset.

> Additional information can be found on Wikipedia or via the original report PDF.

> Additional related datasets can be found at Our World in Data.

> For details around units for yield/magnitude, please see the Nuclear Yield formulas.

# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggradar)
library(gganimate)
library(scales)

# nuclear_explosions <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-20/nuclear_explosions.csv")
#write_csv(nuclear_explosions, "nuclear_explosions.csv")

nuclear_explosions <- readr::read_csv("nuclear_explosions.csv")
```

# Data 

I'm inclined to do a radar chart, a jojo chart, to show the power of the explosions.

```{r}
unique(nuclear_explosions$country)
```

Let's make the chart for the USA for the biggest average yield in each year.

```{r}
nuclear_explosions %>% 
  select(country, year, magnitude_body, magnitude_surface,
         yield_lower, yield_upper) %>% 
  group_by(country, year) %>% 
  filter_all(all_vars(. > 0)) %>% 
  slice(which.max(yield_upper)) %>% 
  ungroup() %>% 
  mutate(count_year = table(year)[as.character(year)]) %>% 
  rename(group = country,
         `yield up` = yield_upper,
         yield_low = yield_lower,
         mangnitude_surf = magnitude_surface) %>% 
  filter(count_year == max(count_year)) %>% 
  select(-c(year, count_year)) %>% 
  mutate_at(vars(-group), rescale) %>% 
  ggradar(
    base.size = 8,
    gridline.min.colour = 'slategrey',
    gridline.mid.colour = 'slategrey',
    gridline.max.colour = 'slategrey',
    grid.label.size = 3,
    axis.label.size = 4,
    axis.line.colour = 'lightslategrey',
    group.line.width = 1.2,
    group.point.size = 4,
    background.circle.colour = 'gainsboro',
    legend.text.size = 9,
    legend.position = 'top'
  )


```

