---
title: "Tidy Tuesday 08/10/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-10-08):

>This week's data is from Open Powerlifting.   
>Wikipedia has many details around the sport itself, as well as more details around the 3 lifts (squat, bench, and deadlift).    
>Credit to Nichole Monhait for sharing this fantastic open dataset. Please note this is a small subset of the data limited to IPF (International Powerlifting Federation) events, the full dataset with many more columns and alternative events can be found as a .csv at https://openpowerlifting.org/data. The full dataset has many more federations, ages, and meet types but is >250 MB.    
>A nice analysis of this dataset for age-effects in R can be found at Elias Oziolor's Blog

# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(Cairo)

ipf_data <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-08/ipf_lifts.csv")

```

# Data 

```{r}
str(ipf_data)
```

I want to find if any equipment is preferred by a certain gender or age group.

```{r inp_smooth, message=FALSE, warning=FALSE, dev='CairoPNG'}
facet_titles <- c(
  'best3squat_kg' = 'Squat',
  'best3bench_kg' = 'Bench',
  'best3deadlift_kg' = 'Deadlift'
)


ipf_data %>% 
  select(sex, age, best3squat_kg, best3bench_kg, best3deadlift_kg) %>% 
  pivot_longer(-c(sex, age), names_to = 'type', values_to = 'best') %>% 
  filter(best > 0) %>% 
  mutate(sex = factor(sex, levels = c('M','F'), ordered = TRUE)) %>% 
  ggplot(aes(age, best)) +
  geom_point(alpha = 1/20, color = 'darkslategrey') +
  geom_smooth(aes(color = sex), se = FALSE) +
  facet_wrap(~type,
             labeller = as_labeller(facet_titles)) +
  scale_color_manual(values = c('blue2', 'red1'),
                     name = 'Gender') +
  xlab('Age') +
  ylab('Weight(kg)') +
  labs(title = 'How maximum lift changes with age?',
      subtitle = 'Patterns for men and women seem similar') + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.placement = 'outside',
        panel.border = element_rect(color = 'lightslategrey'),
        title = element_text(colour = "slategrey"),
        legend.text = element_text(colour = "slategrey"),
        strip.text = element_text(color = 'slategrey'),
        axis.ticks = element_line(color = 'lightslategrey'),
        axis.text = element_text(color = 'lightslategrey')
        )
```

