---
title: "Tidy Tuesday 20/08/2019"
output:
  github_document: 
    df_print: kable
always_allow_html: yes
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-08-13):

> This week's data is from Stockholm International Peace Research Institute, by way of data is plural with credit to Jesus Castagnetto for sharing the dataset.

> Additional information can be found on Wikipedia or via the original report PDF.

> Additional related datasets can be found at Our World in Data.

> For details around units for yield/magnitude, please see the Nuclear Yield formulas.

# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)

# nuclear_explosions <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-20/nuclear_explosions.csv")
#write_csv(nuclear_explosions, "nuclear_explosions.csv")

nuclear_explosions <- readr::read_csv("nuclear_explosions.csv")
```

# Data 

I'm inclined to do a radar chart for the 

```{r}
#View(emperors)
str(emperors, give.attr = FALSE)
```

Most of the data is date or categorical. I'm curious about how many different death causes and killers we have.

```{r}
emperors_ck <- emperors %>% 
  transmute(cause = factor(cause),
         killer = factor(killer))

summary(emperors_ck)
```

So we have just 7 death causes and some varied killer motives, so I can create a treemap to display this information.

Creating a data frame with the relevant information for the treemap.

```{r}
emperors_ck <- emperors_ck %>% 
  transmute(parent = cause,
            id = killer) %>% 
  group_by(parent, id) %>% 
  summarise(value = n())
```

Creating the treemap with treemapify package.

```{r rem_treemap}
ggplot(emperors_ck, aes(area = value, fill = parent,
                        label = id, subgroup = parent))+
  geom_treemap() +
  geom_treemap_text(place = 'topleft', min.size = 8, 
                    reflow = T) +
  geom_treemap_subgroup_text(
    alpha = 0.5, place = 'bottomleft'
  ) +
  scale_fill_brewer(palette = 'Dark2') +
  theme(
    legend.position = 'none',
    title = element_text(colour = 'darkslategrey')
  ) +
  labs(title = 'Cause of death of Roman Emperors (26BC-395AC)')
```

