---
title: "Tidy Tuesday 10/09/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-09-10):

>This week's data is from data.world and the Safer Parks database.

>A lot of free text this week, some inconsistent NAs (n/a, N/A) and dates (ymd, dmy). A good chance to do some data cleaning and then take a look at frequency, type of injury, and analyze free text.

>Additional data can be found at SaferParks Database

# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(waffle)

library(tidytext)
library(wordcloud)

tx_injuries <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-10/tx_injuries.csv")

safer_parks <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-10/saferparks.csv")
```

# Look at data

```{r mol_point, message=FALSE, warning=FALSE}
safer_parks %>% glimpse()
```

Looking at the Source of accidents.

```{r amp_waffle}
(p <- safer_parks %>% 
  summarise(
    mech_count = sum(mechanical, na.rm = TRUE),
    op_error_count = sum(op_error, na.rm = TRUE),
    emp_count = sum(op_error, na.rm = TRUE)
  ) %>% 
  transmute(
    total = sum(mech_count, op_error_count, emp_count),
    `Each box is 1%` = 0,
    Mechanical = round(mech_count/total, digits = 2)*100,
    Operational = round(op_error_count/total, digits = 2)*100,
    Employee = round(emp_count/total, digits = 2)*100,
  ) %>% 
  select(-total) %>% 
  waffle(title = "Source of accidents in Amusement Parks",
         colors = c("lightslategrey" , "#1b9e77", 
                    "#d95f02", "#7570b3")) +
   labs(caption = "Source: SaferParks ") +
   theme(plot.title = element_text(size = 15,
                                  face = "bold",
                                  color = "darkslategrey",
                                  margin = margin(0,0,0,0,'pt'),
                                  hjust = 0.45),
        legend.position = "top",
        legend.margin = margin(0,0,0,0,'pt'),
        legend.spacing = margin(0,0,0,0,'pt'),
        legend.box.spacing = margin(0,1,1,1,'pt'),
        plot.caption = element_text(size = 7,
                                    color = "lightslategrey",
                                    margin = margin(0,0,0,0,'pt')), 
        legend.text = element_text(color = "darkslategrey")
        ))
```

Now looking at the free test to see the most frequent words of the alleged injury reports

```{r}
tx_injuries %>% glimpse()
```

Let's create the barplot.

```{r amp_bar, message=FALSE, warning=FALSE}
tx_injuries %>% 
  select(alleged_injury) %>% 
  unnest_tokens("word", alleged_injury) %>% 
  anti_join(stop_words) %>% 
  count(word, sort = TRUE) %>% 
  mutate(word = reorder(word,n)) %>% 
  filter(word != 'NA') %>% 
  top_n(10, n) %>% 
  ggplot(aes(word, n)) +
  geom_col(fill = "darkred") +
  labs(title = "Most frequent words in alleged injury reports at amusement parks",
       x = "Count",
       y = "Word") +
  scale_y_continuous(expand = c(0,0)) + 
  coord_flip() +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_blank(),
    plot.title = element_text(hjust = -.6,
                              color = "darkslategrey"),
    axis.text = element_text(color = 'darkslategrey'),
    axis.title = element_text(color = 'darkslategrey')
  )

```

