---
title: "Tidy Tuesday 05/11/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
editor_options: 
  chunk_output_type: inline
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-11-05):

>This week's data is from the [ACS Survey](https://www.census.gov/library/publications/2014/acs/acs-25.html?#). The article and underlying data can be found at the [Census Website](https://www.census.gov/library/publications/2014/acs/acs-25.html?#). The PDF report is also available for [download](/data/2019/2019-11-05/acs-25.pdf) if you'd like to try reading in some of the embedded tables.
>
Please note that the raw excel files are uploaded (6 total), along with the cleaned/tidy data (`commute.csv`). There is also a cleaned up version of Table 3 from the article, which incorporates summary data around age, gender, race, children, income, and education for modes of travel (bike, walk, other). If you work with the ACS table 3 I'd suggest `dplyr::slice()` to grab the specific sub-tables from within it!

# Packages and reading data

```{r message=FALSE, warning=FALSE}
library(tidyverse)

commute_mode <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-11-05/commute.csv")
```

# First look

```{r}
commute_mode %>% glimpse()
```

I'll look the percents, state_regions  and city_size.

```{r com_vio}
commute_mode %>% 
  filter(!is.na(state_region)) %>% 
  ggplot(aes(city_size, percent)) +
  geom_violin(color = "white", fill = "snow") +
  stat_summary(fun.y=mean, geom="point", size = 3, aes(group = 1, color = "mean")) +
  labs(
    title = "Walking and Bycicling to work by city size (US 2008-2012)",
    subtitle = "Some small cites walk/bike a lot, but the averages for all city sizes are very close",
    color = NULL,
    x = "City Size",
    y = "Percentage of population (Estimation)",
    caption = "Source: ACS Survey"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_color_manual(values = "darkred")  +
  facet_wrap(~mode) +
  theme_dark() +
  theme(
    title = element_text(colour = "darkslategrey"),
    legend.title = element_text(hjust = .5),
    legend.text = element_text(colour = "darkslategrey"),
    axis.ticks = element_line(color = 'lightslategrey'),
    axis.text = element_text(color = 'darkslategrey'),
    axis.line = element_blank(),
    axis.title.x = element_blank(), 
    panel.background = element_rect(fill = "grey30"),
    strip.background = element_rect(fill = "grey20"),
    legend.key = element_rect(fill = "snow")
  ) 
```

