---
title: "Tidy Tuesday 03/09/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-09-03):

>This week's data is from Wikipedia - by way of the Data Is Beautiful Subreddit.

>Additional info and graphics can be found at Our World in Data.

>Moore's Law: Transistors per microprocessor:    
>The observation that the number of transistors in a dense integrated circuit doubles approximately every two years.

# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(scales)

cpu <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-03/cpu.csv")

gpu <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-03/gpu.csv")

ram <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-03/ram.csv")

```

Let's see number of transistors over time.

```{r mol_point, message=FALSE, warning=FALSE}

ggplot(mapping = aes(date_of_introduction, transistor_count)) + 
  geom_point(data = ram, aes(color = 'ram')) + 
  geom_point(data = gpu, aes(color = 'gpu')) +
  geom_point(data = cpu, aes(color = 'cpu')) + 
  labs(
    title = "Number of transistors went up exponentially",
    y = "Log of number of transistors",
    color = "Type of \nmicroprocessor"
    ) +
  scale_y_log10(labels = trans_format("log10", math_format(10^.x))) + 
  scale_colour_brewer(palette = 'Set2') +
  theme_bw() +
  theme(
        title = element_text(colour = "darkslategrey"),
        legend.title = element_text(hjust = .5),
        panel.grid = element_blank(),
        legend.text = element_text(colour = "darkslategrey"),
        axis.ticks = element_line(color = 'lightslategrey'),
        axis.text = element_text(color = 'lightslategrey'),
        axis.line = element_blank(),
        axis.title.x = element_blank()
        )
```

