---
title: "Tidy Tuesday 22/10/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
editor_options: 
  chunk_output_type: inline
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-10-22):

>This week's data is from the [IMDB](https://www.kaggle.com/PromptCloudHQ/imdb-horror-movie-dataset) by way of Kaggle.
>
>H/t to [Georgios Karamanis](https://twitter.com/geokaramanis) for sharing the data this week.
>
>Thrillist did a [75 Best Horror Movies of all Time article](https://www.thrillist.com/entertainment/nation/best-horror-movies-ever). There's also a [Stephen Follows article](https://stephenfollows.com/what-the-data-says-about-producing-low-budget-horror-films/) about horror movies exploring data around profit, popularity and ratings.
>
>Last year for Halloween we focused on Horror Movie Profit - feel free to take a peek at that data as well on [our GitHub](https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-10-23).


# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse) #data collection, manipulation and plots
library(tidytext) #text manipulation
library(scales) #number format transforming
library(here) #make sure the figures are in the right place
library(RCurl) #because curl is giving me a headache

horror_movies <- readr::read_csv(RCurl::getURL(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-22/horror_movies.csv"
  ))

```

# Data 

```{r}
glimpse(horror_movies)
```

I think I'll go for some text mining and look for the plots. First some tokenizing.

```{r}
#creating a ata frame with digrams
horror_token <- horror_movies %>% 
  select(plot, genres) %>%
  unnest_tokens("genre", genres, token = "ngrams", n =2) %>% 
  filter(str_detect(genre, "fi", negate = TRUE),
         str_detect(genre, "horror")) %>% 
  distinct()
```

I'll make a pie chart with the proportion of released movies in all years. But first I have to create the labels.

```{r}
#vector with the 5 most common digrams
most_common <- horror_token %>% 
  group_by(genre) %>% 
  summarise(n = n()) %>% 
  top_n(5, n) %>% 
  select(genre) %>% 
  as_vector() %>% 
  unname()

#fucntion to capitalize categories. Stolen from R 
 .simpleCap <- function(x) {
    s <- strsplit(x, " ")[[1]]
    paste(toupper(substring(s, 1, 1)), substring(s, 2),
          sep = "", collapse = " ")
}

```

Then I create a table with the proportion of each of the selected categories.

```{r hom_pie, dev = "png", dev.args=list(bg='transparent')}
 horror_token %>% 
  mutate(top = case_when(
    genre == "horror sci" ~ "Sci-fi",
    genre %in% most_common ~  str_remove(genre, "\\s?horror\\s?"),
    TRUE ~ "Other"
  )) %>%
  group_by(top) %>%
  count() %>% 
  ungroup() %>% 
  transmute(n = n/sum(n),
            top = map_chr(top, .simpleCap),
         top = fct_reorder(top, n)) %>% 
  ggplot(aes(x = "", y = n, fill = top)) +
  geom_bar(stat = "identity", width = 1, size = 1, color = "grey30") +
  geom_text(aes(label = percent(n, accuracy = 1)),
            position = position_stack(vjust = .55),
            color = "snow") +
  labs(
    title = "Rejoice horror fans... \'cause it\'s thriller night", 
    subtitle = "Thriller is the genre that most appears associated with horror at imdb",
    fill ="Other category \nin horror movies"
  ) +
  guides(fill = guide_legend(reverse = TRUE, override.aes = c(size = .5))) +
  scale_fill_manual(values = c("#FF8500", "#090714", "#792B17",
                               "#7C12A6", "#2A361E", "#181393")) +
  coord_polar("y", start = 0) +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "grey20"),
    plot.title = element_text(color = "snow", face = "bold"),
    plot.subtitle = element_text(color = "snow"),
    panel.grid = element_blank(),
    legend.background = element_rect(fill = "grey20",
                                     color = "grey20"),
    legend.text = element_text(color = "snow"),
    legend.title = element_text(color = "snow"),
    legend.box.margin = margin(1,3,1,1),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank()
  )
```

