---
title: "Tidy Tuesday 03/02/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
editor_options: 
  chunk_output_type: inline
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-12-03):

>This week's data is from [Open Data Philly](https://www.opendataphilly.org/dataset/parking-violations) - there is over 1 GB of data, but I have filtered it down to <100 MB due to GitHub restrictions. I accomplished this mainly by filtering to data for only 2017 in Pennsylvania that had lat/long data. If you would like to use the entire dataset, please see the link above.
>
H/t to [Jess Streeter](https://twitter.com/phillynerd) for sharing this week's data!
>
Some visualizations from [Philly Open Data](https://data.phila.gov/visualizations/parking-violations) and a news article by [NBC Philadelphia](https://www.nbcphiladelphia.com/news/local/Nearly-6-Million-Philadelphia-Parking-Authority-Tickets-Are-on-the-Rise-Since-2016-565438131.html).

# Packages and data reading

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(patchwork)

tickets <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-03/tickets.csv")

```

# Quick look

```{r}
tickets %>% glimpse()
```

How many types of violations?

```{r phi_poi-1, dev='CairoPNG'}
means <- tickets %>% 
  filter(!is.na(issuing_agency)) %>% 
  group_by(issuing_agency) %>% 
  summarise(mean_fine = mean(fine)) %>%
  mutate(housing_ppa = ifelse(issuing_agency %in% c('HOUSING', 'PPA'),
                              'Y', 'N')) %>% 
  ggplot(aes(reorder(issuing_agency, mean_fine), mean_fine, 
             color = housing_ppa)) +
  geom_point(size = 4) +
  labs(
    title = 'Housing fines are high',
    subtitle = 'While PPA\'s bottom in value',
    x = 'Issuing Agency',
    y = 'Average fine value'
  ) +
  coord_flip() +
  scale_y_continuous(labels = scales::dollar_format()) +
  scale_color_manual(values = c('darkslategrey', 'navyblue'), guide = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.placement = 'outside',
        panel.border = element_rect(color = 'lightslategrey'),
        title = element_text(colour = "darkslategrey"),
        strip.text = element_text(color = 'slategrey'),
        axis.ticks = element_line(color = 'lightslategrey'),
        axis.text = element_text(color = 'slategrey'))

means
```


```{r phi_poi-2, dev='CairoPNG'}
total_log <- tickets %>% 
  filter(!is.na(issuing_agency)) %>%
  group_by(issuing_agency) %>% 
  summarise(sum_fine = sum(fine)) %>%
  mutate(housing_ppa = ifelse(issuing_agency %in% c('HOUSING', 'PPA'),
                              'Y', 'N')) %>% 
  ggplot(aes(reorder(issuing_agency, sum_fine), sum_fine,
             color = housing_ppa)) +
  geom_point(size = 4) +
  labs(
    title = 'But PPA collects more money',
    subtitle = 'More than 100 times Housing\'s',
    x = NULL,
    y = 'Total collected (log scale)'
  ) + 
  coord_flip() +
  scale_y_log10(labels = scales::label_number_si(prefix = '$')) +
  scale_color_manual(values = c('darkslategrey', 'navyblue'), guide = FALSE) +
  theme_bw() + 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.placement = 'outside',
        panel.border = element_rect(color = 'slategrey'),
        title = element_text(colour = "darkslategrey"),
        strip.text = element_text(color = 'slategrey'),
        axis.ticks = element_line(color = 'lightslategrey'),
        axis.text = element_text(color = 'slategrey'))

total_log
```


Using patchwork to get the plots together.

```{r phi_poi-3, dev='CairoPNG'}
final_plot <- means + total_log +
  plot_annotation(
    title = 'Volume > Value when talking abour Parking Violation Fines',
    subtitle = 'In Philadelphia PPA collects more money from parking tickets besides lowest value for fines issued',
    caption = 'Data from Open Data Philly for 2017',
    theme = theme(
      plot.title = element_text(color = 'darkslategrey'),
      plot.subtitle = element_text(color = 'darkslategrey'),
      plot.caption = element_text(color = 'lightslategrey')
      )
    )

final_plot
```

