---
title: "Tidy Tuesday 17/09/2019"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-09-10):

>This week's data is from data.world and the Safer Parks database.

>A lot of free text this week, some inconsistent NAs (n/a, N/A) and dates (ymd, dmy). A good chance to do some data cleaning and then take a look at frequency, type of injury, and analyze free text.

>Additional data can be found at SaferParks Database

# Import data and packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)

tx_injuries <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-10/tx_injuries.csv")

safer_parks <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-10/saferparks.csv")
```
