---
title: "Tidy Tuesday 14/01/2020"
output:
  github_document: 
    df_print: tibble
always_allow_html: yes
editor_options: 
  chunk_output_type: inline
---

```{r opts, echo = FALSE}
figs_path <- paste0(here::here("docs", "assets", "images"),"/")
knitr::opts_chunk$set(
  fig.path = figs_path
)
```

# Data description

From From [TidyTuesdays github](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-01-14):

>This week's data is all about passwords. Data is sourced from [Information is Beautiful](https://docs.google.com/spreadsheets/d/1cz7TDhm0ebVpySqbTvrHrD3WpxeyE4hLZtifWSnoNTQ/edit#gid=21), with the graphic coming from the same group [here](https://twitter.com/infobeautiful/status/1216765612439019521?s=20).
>
There's lots of additional information about password quality & strength in the source [Doc](https://docs.google.com/spreadsheets/d/1cz7TDhm0ebVpySqbTvrHrD3WpxeyE4hLZtifWSnoNTQ/edit#gid=21). Please note that the "strength" column in this dataset is relative to these common aka "bad" passwords and YOU SHOULDN'T USE ANY OF THEM!
>
[Wikipedia](https://en.wikipedia.org/wiki/Password_strength) has a nice article on password strength as well.

# Packages and data reading

```{r message=FALSE, warning=FALSE}
library(tidyverse)

passwords <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-14/passwords.csv') %>% 
  drop_na()
```

# Quick look

```{r}
passwords %>% glimpse()
```

How many categories?

```{r phi_poi-1, dev='CairoPNG'}
passwords %>% 
  count(category)
```


```{r phi_poi-2, dev='CairoPNG'}
value_to_sec <- setNames(c(365*24*60*60, 60, 24*60*60, 1, 30*24*60*60, 
                         7*24*60*60, 60*60),
                       passwords$time_unit %>% unique())
plain <- function(x,...) {
  format(x, ..., scientific = FALSE, drop0trailing = TRUE)
}

y_labels <- value_to_sec
names(y_labels) <- str_c("1", str_remove(names(value_to_sec), "s$"), sep = " ")

passwords %>%
  mutate(value_sec = value*value_to_sec[time_unit]) %>% 
  # filter(offline_crack_sec < 25) %>% 
  ggplot() +
  geom_count(aes(offline_crack_sec, value_sec)) +
  scale_x_log10(labels = plain) +
  scale_y_log10(breaks = y_labels) +
  labs(
    title = "When talking password security, beware offline cracking",
    subtitle = "Gain in security for offline cracking is much smaller compared with guessing's",
    x = "Offline cracking time (seconds)",
    y = "Online guessing\ncracking time",
    size = "Number of\npasswords"
  ) +
  ggthemes::theme_solarized_2() +
  theme(
    axis.title.y = element_text(angle = 0, hjust = 0),
    plot.title.position = "plot",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
    )
```

```{r}
sort(value_to_sec)
```

