---
title: "The Last Airbender"
author: "Jorge Mendes"
date: "10/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidy tuesday last airbender

```{r}
library(tidyverse)
library(tidytext)
library(stopwords)
library(gghighlight)
library(tvthemes)
library(patchwork)

avatar <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-11/avatar.csv')

```


Reading data from Zuko

```{r}
data("stop_words")

avatar_words <- avatar %>% 
  select(book, chapter, chapter_num, character,
         character_words, imdb_rating) %>% 
  filter(character != "Scene Description") %>% 
  group_by(book) %>% 
  mutate(line_num = row_number()) %>% 
  ungroup() %>% 
  unnest_tokens(word, character_words) %>% 
  anti_join(stop_words)
```
# Dataframe of Zuko words

```{r}
zuko_words <- avatar %>% 
  filter(character == "Zuko") %>% 
  mutate(zuko_journey = case_when(
    book == "Water" ~ 'Search for the Avatar\n(Book 1)',
    book == "Earth" ~ 'Traitor of the Fire Nation\n(Book 2)',
    book == "Fire" & chapter_num <= 11 ~ 'Prince of the Fire Nation\n(Book 3 Episodes 1-11)',
    TRUE ~ "Avatar's teacher\n(Book 3 Episodes 11-24)"
  ),
  zuko_journey = factor(zuko_journey, 
                        c('Search for the Avatar\n(Book 1)', 
                          'Traitor of the Fire Nation\n(Book 2)',
                          'Prince of the Fire Nation\n(Book 3 Episodes 1-11)', 
                          "Avatar's teacher\n(Book 3 Episodes 11-24)"))) %>% 
  select(chapter, chapter_num, zuko_journey,
         character_words, imdb_rating) %>% 
  group_by(zuko_journey) %>% 
  mutate(line_num = row_number()) %>% 
  ungroup() %>% 
  unnest_tokens(word, character_words) %>% 
  anti_join(stop_words)

#Water - Hunt for the avatar
#Earth - Fugitive
#Fire - Prince of the fire nation 11-
#Fire - Avatar's firebending teacher 11-21
```
# Function with full highlight

Function is messy :(. Look into it later.

```{r}
highlighted_terms <- list(
  c("uncle", "avatar", "home"),
  c("tea", "azula"),
  c("father", "uncle", "dad"),
  c("fire", "uncle", "father", "firebending")
  
)
palette_list <- c("WaterTribe", "EarthKingdom", "FireNation", "FireNation")


zuko_plot <- unique(zuko_words$zuko_journey)

plot_maker <- function(plot_number, highlighted_part = 0){
  
  #helper to make sure plots 3 and 4 display colors as intended
  is_selected_levels <- if(plot_number < 3) c("TRUE", "FALSE") else c("FALSE", "TRUE")
  
  plot_palette <- avatar_pal(palette = palette_list[plot_number])(2)
  #helper to make sure plots 3 and 4 display colors as intended
  plot_palette <-   if(plot_number < 3) plot_palette else rev(plot_palette)
  
  #filtering only if there's a highlight in the plot
  is_selected_column <- if(highlighted_part == 0 | highlighted_part == zuko_plot[plot_number]) quo(is_selected) else quo(NULL)
  
  plot_df <- zuko_words %>% 
    filter(zuko_journey == zuko_plot[plot_number]) %>% 
    count(word, sort = TRUE) %>%
    slice(1:7) %>% 
    ungroup() %>% 
    mutate(is_selected = factor(word %in% highlighted_terms[[plot_number]],
                                is_selected_levels),
           word = reorder(word, n))
  
  plot_object <- plot_df %>% 
    ggplot(aes(x = n, y = word, fill = !!is_selected_column)) +
    geom_col(aes_string()) +
    scale_fill_manual(guide = NULL, values = plot_palette) +
    scale_y_reordered() +
    scale_x_continuous(expand = expansion(mult=c(.01, .1))) +
    labs(title = zuko_plot[plot_number],
         x = "Count",
         y = "Words Spoken") +
    theme_avatar(title.size = 14,
                 axis.text.size = 9,
                 axis.title.size = 11) 
  
  if(highlighted_part == 0 | highlighted_part == zuko_plot[plot_number]){
  
    plot_object <- plot_object + gghighlight(word %in% highlighted_terms[[plot_number]],
                unhighlighted_params = list(
                  fill = alpha(plot_palette[2], alpha = .2))
    )
  }
  
  plot_object
  
}


```

Complete colored plot

```{r}
#makes all 4 plots
avatar_plots <- map(1:4, plot_maker)

complete_plot <- (avatar_plots[[1]] + avatar_plots[[2]]) / (avatar_plots[[3]] + avatar_plots[[4]]) +
  plot_annotation(
    title = "Zuko's most common words changed as his plot progressed",
    subtitle = "But Uncle Iroh remained constant",
    caption = "By @jorgelsm for #TidyTuesday",
    theme = theme(
      plot.background = element_rect(color = NA, 
        fill = "#ece5d3"), 
      panel.background = element_rect(color = NA, 
        fill = "#ece5d3")
    )
  )
complete_plot
```



Calling for partial highlighted plots. Changing the value of zuko_plot changes the colored plot.

```{r}
avatar_plots <- map(1:4, plot_maker, zuko_plot[4])

partial_plot <- (avatar_plots[[1]] + avatar_plots[[2]]) / (avatar_plots[[3]] + avatar_plots[[4]]) +
  plot_annotation(
    title = "Zuko's most common words changed as his plot progressed",
    subtitle = "But Uncle Iroh remained constant",
    caption = "By @jorgelsm for #TidyTuesday",
    theme = theme(
      plot.background = element_rect(color = NA, 
        fill = "#ece5d3"), 
      panel.background = element_rect(color = NA, 
        fill = "#ece5d3")
    )
  )

partial_plot
```
# Twitter text

* For #TidyTuesday with Last Airbender data I've decided to make a plot from my favorite character arch in the cartoon, Zuko's.
I separated his plot into some parts and highlighted few words that I felt important for each section.

* In the first book most of the words are related to his search and current state, such as avatar and ship. Uncle Iroh is from the beginning a powerful presence in his life.

* In Book 2 we can see the start of his personal conflict. Azula and tea represent the paths in front of him. Azula, whom he envies and pursues him, is his connection to his past. While tea represents his uncle's desire for a more peaceful life, opening a tea shop.

* On the first half of Fire book his relationship and worries about his father are more present. He questions his place of the fire nation and its existence.

* In the second half, the role of fire nation and firebending are addressed. His uncle and dad now represents the path he's chosen and the one he's left behind.